Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 response_to_reviewers.tex

\begin{quote}
\color{blue}
We corrected the word from ``variation'' to ``rate''.
\end{quote}

\textbf{19. Reviewer's Comment:}
Page 7, third paragraph of Discussion: Replace “This is the reason why” with
“The relatively low phylogenetic support for many nodes in the Nymphalidae tree
is likely the reason why”.

\textbf{19. Response:}

\begin{quote}
\color{blue}
We modified the sentence according to the reviewer's suggestion.
\end{quote}

\textbf{20. Reviewer's Comment:}
Page 7, fourth paragraph of Discussion: Omit this paragraph.

\textbf{20. Response:}

\begin{quote}
\color{blue}
We removed the paragraph according to the reviewer's suggestion.
\end{quote}

\textbf{21. Reviewer's Comment:}
Pages 7-8, fourth paragraph of Discussion: Per previous comment of BAMM analysis, this paragraph should probably be removed. If it is not, both shifts detected by BAMM analysis (not just one) should be described and compared to the four identified in MultiMEDUSA (are they at the same nodes or different nodes?).

\textbf{21. Response:}

\begin{quote}
\color{blue}
We removed the paragraph according to the reviewer's suggestion.
\end{quote}

\end{document}

### 2015-01-14 MS_revised.tex
comment 20
comment 21
comment 22

The clade Ithomiini and the non-basal danaids are well supported by high
posterior probability values in Wahlberg et al. (2009) \cite{wahlberg2009}.
Therefore our MEDUSA analyses recovered an increase in net
diversification rate with probability higher than 0.90 in the posterior
distribution of trees (Fig. 3).

@@

The increase in diversification inferred by MEDUSA occurred after the
probable shift from Apocynaceae to Solanaceae, as the Solanaceae feeders
in the subtribes Melinaeina and Mechanitina are not included in the
diversification shift (shift number 5 in Fig. 1). The apparent
conflicting results from MEDUSA and BiSSE can be explained by the low
species-richness of the subtribes Melinaeina and Mechanitina compared to
the other subtribes included in the shift (52 versus 272 species). It
can be that MEDUSA is more conservative than BiSSE and is not including
Melinaeina and Mechanitina in the shift due to low species numbers.

>>>>

@@

The increase in diversification rate inferred by MEDUSA occurred after the
probable shift from Apocynaceae to Solanaceae, as the Solanaceae feeders
in the subtribes Melinaeina and Mechanitina are not included in the
diversification shift (shift number 5 in Fig. 1). The apparent
conflicting results from MEDUSA and BiSSE can be explained by the low
species-richness of the subtribes Melinaeina and Mechanitina compared to
the other subtribes included in the shift (52 versus 272 species). It
can be that MEDUSA is more conservative than BiSSE and is not including
Melinaeina and Mechanitina in the shift due to low species numbers.
